### 2016-02-08 Irregular-occ/Irregular-occ.tex
.

Since 2009 many successful observations of stellar occultations by TNOs have been reported in the literature \citep{Elliot2010, Sicardy2011, Ortiz2012, Braga-Ribas2013}, the main disadvantages in their prediction being large heliocentric distances and ephemeris error, facts somewhat compensated for the larger diameters involved. However, in the case of irregular satellites, we have much better ephemeris because the orbits of their host planets are better known, their observational time span is much wider and covers many orbital periods in contrast to TNOs. Moreover, the irregular satellites are much closer to Earth which implies in a much smaller shadow path error in kilometers. These advantages may be somewhat balanced by the smaller sizes estimated for the irregular satellites.Thus, in comparison, the chances for a successful observation of an stellar occultation by an irregular satellite should be considered at least also as good as those by TNOs.

@@

Here we develop our own ephemeris based on the observations published in \cite{GomesJunior2015}. First because many of the authors of this paper worked in the production of that set of positions, so that it was very well known. Second, besides recent observations, this consistent set of numerous and precise positions covers many orbital periods at many distinct orbital plane sights, so that the orbital inclinations along with all other orbital elements could be satisfactorily derived without the need of further position sets. For these reasons, only this set of positions was used for building the new ephemeris for the satellites of Jupiter.

>>>>

Since 2009 many successful observations of stellar occultations by TNOs have been reported in the literature \citep{Elliot2010, Sicardy2011, Ortiz2012, Braga-Ribas2013}, the main disadvantages in their prediction being large heliocentric distances and ephemeris error, facts somewhat compensated for the larger diameters involved. In contrast to TNOs, the irregular satellites have much better ephemeris because the orbits of their host planets are better  known, their observational time span is much wider and covers many orbital periods. Moreover, the irregular satellites are much closer to Earth which implies in a much smaller shadow path error in kilometers. These advantages may be somewhat balanced by the smaller sizes estimated for the irregular satellites.Thus, in comparison, the chances for a successful observation of an stellar occultation by an irregular satellite should be considered at least also as good as those by TNOs.

@@

Here we develop our own ephemeris based on the observations published in \cite{GomesJunior2015}. First, because the reduction was made with consistent and precise stellar catalogue and with a robust and reliable software (PRAIA, \cite{Assafin2011}). Second, besides recent observations, this consistent set of numerous and precise positions covers many orbital periods at many distinct orbital plane sights, so that the orbital inclinations along with all other orbital elements could be satisfactorily derived without the need of further position sets. For these reasons, only this set of positions was used for building the new ephemeris for the satellites of Jupiter.
